---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center",
  out.width = "50%"
)
```
# wspviz

<!-- badges: start -->
<!-- badges: end -->

Utilities for common R visualization tasks at WSP Finland.
Current features:

- Color palettes for WSP and [HSL](https://hsl.fi/tyyliopas) colors

Planned features:

- Tailored `ggplot2` themes for WSP and other common contexts

## Installation

Ensure you have [`devtools`](https://github.com/r-lib/devtools) installed.
To get the latest development version of `wspviz`,
run the following command:

``` r
devtools::install_github("webbidevaajat/wspviz")
```

Current version depends on `ggplot2` library
(because of `show_palettes()` function).

## Examples

Get all the HSL colors as a named vector:

```{r example1, message=FALSE, warning=FALSE}
library(wspviz)
pal_hsl()
```

Get selected WSP colors:

```{r example2, message=FALSE, warning=FALSE}
library(wspviz)
pal_wsp("red", "blue", "gray")
```

Plot a color palette:

```{r example3, message=FALSE, warning=FALSE}
library(wspviz)
show_palette(pal_wsp())
```

If you are for some reason running the palette functions
several times, say, generating 1000 different plots,
you can extract the color codes and just use
named vector subsetting for a slight performance benefit
(comparison has not been made so far), like this:

```{r example, message=FALSE, warning=FALSE}
library(wspviz)
pal <- pal_hsl()
show_palette(pal[c("bus", "tram", "train", "metro", "ferry")])
# Instead of show_palette(pal_wsp("purple", "midnightblue"))
```
